\mythesistitleNOTSYNPOSIS \tnote[fyi]{Synopsis title is ``Generalization of Consecutive Ones Property of Binary Matrices''}

### 2012-02-24 src/003abstract.tex
- a whole bunch of cleanups. see diff. - removed problem defs from chap 1. they were duplicates from chap 3. - CODED FIGURES IN TIKZ. forbidden subgraphs, graphmatrix example graphs. - BEGAN CHAPTER 3 EDITS.
Formatting/layout changes
-------

- Added FrenchLayout to make lists denser
- Added hanging indent for Definitions
- Compressed theorem env's above below spaces
- Creaded env for problem definition minipages.
- moved all clearpage/page counter and other prechapter settings to the chapter tex files.
- Fixed the page number bug in draft printout. removed \fancyhf{} to avoid resetting page n

  \def \tem {}
  \noindent
  Consecutive-ones property is a non-trivial property of binary
  matrices that has been studied widely in the literature for over
  past 50 years. Detection of COP in a matrix is possible efficiently
  and there are several algorithms that achieve the same. This thesis
  documents the work done on an extension of COP extended from the
  equivalent interval assignment problem in \cite{nsnrs09}. These new
  results rigorously prove a natural extension (to trees) of their
  characterization as well as makes connections to graph isomorphism,
  namely path graph isomorphism.

  \tnote{EXPAND.  Abstract must be a brief about what results we have
    and how it fits
    in the body of research.\\
    -- Area: Broad to Specialized. i.e. Combinatorial algorithms ->
    Matrix reorganization -> general data reorganization
    (interval assignment) -> path assignment\\
    -- Class of problems: say, data reorganization.\\
    -- Nature of results: Is a generalization. We have a
    Polynomial algorithm for a subset of the generalization.\\
    % maybe add - we explore a natural generalization of results on
    % binary matrices with the |\tem consecutive-ones property|.  We
    % consider the following constraint satisfaction problem. Given
    % (i) a set system $\F \subseteq$ $(2^{U} \setminus \emptyset)$ of
    % a finite set $U$ of cardinality $n$, (ii) a tree $T$ of size $n$
    % and (iii) a bijection called |\tem tree path labeling|, $\cl$
    % mapping the sets in $\cF$ to paths in $T$, does there exist at
    % least one bijection $\phi:U \rightarrow V(T)$ such that for each
    % $S \in \cF$, $\{\phi(x) \mid x \in S\} = \cl(S)$?  A tree path
    % labeling of a set system is called |\tem feasible| if there
    % exists such a bijection $\phi$.  We present an algorithmic
    % characterization of feasible tree path labeling. COP is a
    % special instance of tree path labeling problem when $T$ is a
    % path.  We conclude with a polynomial time algorithm to find a
    % feasible tree path labeling of a given set system when $T$ is a
    % |\tem $k$-subdivided star|, set system has a single containment
    % tree of overlap components and set size is limited to at most
    % $k+2$.
  }
\end{abstract}

>>>>

  \def \tem {}
  \noindent
  Consecutive-ones property is a non-trivial combinatorial property of
  binary matrices that has been studied widely in the literature for
  over past 50 years. Detection of COP in a matrix is possible
  efficiently and there are several algorithms that achieve the
  same. This thesis documents the work done on an extension of COP.
  We extend \COP from the equivalent interval assignment problem to what we
  call {\em Tree Path Labeling (TPL)} problem. Inspired by the idea
  that \COP is akin to assigning intervals to sets in a set system, we
  ask the question what if the assignments to sets are made not of
  intervals but of paths from any tree?  While we show that TPL is in
  NP, we obtain a more efficient algorithm for a special case tree
  class called {\em $k$-subdivided stars} as well as for
  characterizing a feasible TPL. For extension of \COP to
  arbitrary trees, we analyse the structure of a hypergraph (set
  system / columns of matrix) using the idea of prime submatrices and
  yield an algorithm for a feasible path labeling if one indeed
  exists.  These new results rigorously prove the natural extension
  (to trees) of the ICPIA characterization as well as makes
  connections to graph isomorphism, namely path graph isomorphism.

  \noindent
  Moreover, this thesis discusses the significance of \COP and the
  evolution of existing data structures and algorithms used in
  detection of \COP over the years -- from \PQtrees to Intersection
  Cardinality Preserving Interval Assignment (ICPIA) data
  structure. We draw conclusions and connections of which some of them
  (for instance, \PQRtree and generalized \PQtree) have not be
  observed before, to the best of our knowledge. This includes the
  fact that \COP can be tested in logspace.

\end{abstract}
